---
title: "Codes for Report"
author: "Team Cool"
date: "3/20/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = FALSE)
```

```{r library, warning=FALSE}
library("readxl")
library("dplyr")
library("stringr")
library(tidyverse)
library(Hmisc)
library(VIM)
library(glmnet)
library("MASS")
library(ROCR)
library("randomForest")
```


```{r import data, message=FALSE, warning=FALSE,tidy=TRUE,results='hide'}

#Tournament 
tour_shoot<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Shooting",col_names = TRUE,skip = 11,col_types = c(rep("text",3), rep("numeric",14), "text", rep("numeric",7)))

tour_pass<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Passing",col_names = TRUE,skip = 11)

tour_defense<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Defense",col_names = TRUE,skip = 11)

tour_goalkeep<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Goalkeeping",col_names = TRUE,skip = 11)

#salary
salary20<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "2020 Salaries",col_names = TRUE,skip = 11)

salary21<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "2021 Salaries",col_names = TRUE,skip = 11)

#Tournament ranks for national teams
rank20<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Results",col_names = TRUE,range = "B11:C27")
colnames(rank20)<-c("rank20","country")

rank21<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "Tournament Results",col_names = TRUE,range = "E11:F35")
colnames(rank21)<-c("rank21","country")

#League
lea_shoot<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "League Shooting",col_names = TRUE,skip = 11)

lea_pass<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "League Passing",col_names = TRUE,skip = 11)

lea_defense<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "League Defense",col_names = TRUE,skip = 11)

lea_goalkeep<-read_excel("/Users/apple/Desktop/ACTL5100 Project/2022-student-research-case-study-player-data.xlsx",sheet = "League Goalkeeping",col_names = TRUE,skip = 11)


```

```{r missing data, message=FALSE, warning=FALSE,tidy=TRUE,results='hide'}
colSums(is.na(tour_shoot)) #large amount of missing
colSums(is.na(tour_pass)) #Total Cmp% 5,Short Cmp% 13,Medium Cmp% 21,Long Cmp% 45
colSums(is.na(tour_defense)) #Vs Dribbles Tkl% 135, Pressures % 26
colSums(is.na(tour_goalkeep)) #Performance Save% 3,Performance CS% 5,Kicks Save% 88
colSums(is.na(salary20)) #no missing
colSums(is.na(salary21)) #no missing

#plot missing data

tour_shoot %>%
  visdat::vis_miss(warn_large_data = FALSE)

tour_pass %>%
  visdat::vis_miss(warn_large_data = FALSE)

tour_defense %>%
  visdat::vis_miss(warn_large_data = FALSE)

tour_goalkeep %>%
  visdat::vis_miss(warn_large_data = FALSE)
#remove penalty kicks save%

tour_shoot%>%count(Year==2020) #tour_shoot: 488 data in 2021, 1527 data in 2020
tour_goalkeep%>%count(Year==2020) #tour_goalkeep: 25 data in 2021, 104 data in 2020
#tour_defense,tour_pass only have data for 2021
#only use 2021 data in tour_shoot, combine dataset with tour_pass and tour_defense:build a model
#tour_goalkeep: build a model(include 2020 and 2021 data)

tour_shoot21<-tour_shoot%>%filter(Year==2021)
tour_shoot20<-tour_shoot%>%filter(Year==2020)

tour_goalkeep21<-tour_goalkeep%>%filter(Year==2021)
tour_goalkeep20<-tour_goalkeep%>%filter(Year==2020)

colSums(is.na(tour_shoot21)) 
tour_shoot21 %>%
  visdat::vis_miss(warn_large_data = FALSE)

colSums(is.na(tour_goalkeep21)) 
tour_goalkeep21 %>%
  visdat::vis_miss(warn_large_data = FALSE)
```

# remove variables with high percentage of missing and check the correlations
## tour_shoot: 
remove:League,year

Correlation matrix to check multi-collinearity and find representative ones:

* Age-Born(remove Born)
* Standard Sh-Standard Sh/90(remove Standard Sh)
* Standard SoT-Standard SoT/90(remove Standard SoT)
* Standard G/Sh-Standard G/SoT(remove Standard G/SoT)
* Expected xG-Expected npxG(remove expected npxG)
* Expected G-xG - Expected np:G-xG(remove Expected G-xG )


## tour_pass:
remove: League,year

Correlation matrix to check multi-collineary and find representative ones:

* remove Born
* Total Att~Total Cmp (remove Total Att)
* Short Att~Short Cmp (remove Short Att)
* Medium Att~Medium Cmp (remove Medium Att)
* Long Att~Long Cmp (remove Long Att)
* A-xA ~ Axt remove A-xA

## tour_denfense
remove: league, year

correlation matrix check: 

* remove Born
* tackles Tkl ~ tackles def 3rd+ tackles mid 3rd+tackles att 3rd (remove tackles Tkl)
* Pressure Press ~ Pressure def 3rd+ Pressure mid 3rd+Pressure att 3rd (remove * Pressure Press)
* remove Blocks Blocks (similar reason)

 
## tour_goalkeep
remove: league, born,year

correlation matrix check:

* Playing Time MP
* Playing Time Starts  
* Playing Time Min
* Performance GA 
* performance cs%
* Penalty Kicks PKA
* Penalty Kicks Save% (60% missing)

```{r message=FALSE, warning=FALSE,tidy=TRUE,results='hide',eval=FALSE}
#tour_shoot
cor_shoot<-cor(tour_shoot21[,-c(1,2,3,18,19)],use = "pairwise.complete.obs")
corrplot::corrplot(cor_shoot)

#tour_pass
cor_pass<-cor(tour_pass[,-c(1,2,3,29,30)],use = "pairwise.complete.obs")
corrplot::corrplot(cor_pass)

#tour_defense
cor_defense<-cor(tour_defense[,-c(1,2,3,30,31)],use = "pairwise.complete.obs")
corrplot::corrplot(cor_defense)

cor(tour_defense$`Vs Dribbles Tkl`/tour_defense$`Vs Dribbles Att`,tour_defense$`Vs Dribbles Tkl%`,use = "pairwise.complete.obs")

cor(tour_defense$`Pressures Succ`/tour_defense$`Pressures Press`,tour_defense$`Pressures %`,use = "pairwise.complete.obs")

#tour_goalkeep
cor_goalkeep<-cor(tour_goalkeep[,-c(1,2,3,25)],use = "pairwise.complete.obs")
corrplot::corrplot(cor_goalkeep)

cor(tour_goalkeep$`Performance Saves`/tour_goalkeep$`Performance SoTA`,tour_goalkeep$`Performance Save%`,use = "pairwise.complete.obs")

```

```{r message=FALSE, warning=FALSE,tidy=TRUE,results='hide'}

#shoot
#remove some variables(highly linearly correlated)
tour_shoot1<-tour_shoot21[,-c(5,8,9,14,18,19,22,24)]
colSums(is.na(tour_shoot1))

#imputation with KNN method(optional)
set.seed(111)
tour_shoot1.impute<-kNN(tour_shoot1,weightDist = TRUE,imp_var = FALSE)



#pass
#remove some useless variables
tour_pass1<-tour_pass[,-c(5,8,13,16,19,23,29,30)]
colSums(is.na(tour_pass1))

#imputated dataset(optional)
#impute the Total/Short/Medium/Long Cmp% by definition
tour_pass.impute<-tour_pass
tour_pass.impute$`Total Cmp%`<-ifelse(is.na(tour_pass.impute$`Total Cmp%`)==1,tour_pass.impute$`Total Cmp`/tour_pass.impute$`Total Att`,tour_pass.impute$`Total Cmp%`)

tour_pass.impute$`Short Cmp%`<-ifelse(is.na(tour_pass.impute$`Short Cmp%`)==1,tour_pass.impute$`Short Cmp`/tour_pass.impute$`Short Att`,tour_pass.impute$`Short Cmp%`)

tour_pass.impute$`Medium Cmp%`<-ifelse(is.na(tour_pass.impute$`Medium Cmp%`)==1,tour_pass.impute$`Medium Cmp`/tour_pass.impute$`Medium Att`,tour_pass.impute$`Medium Cmp%`)

tour_pass.impute$`Long Cmp%`<-ifelse(is.na(tour_pass.impute$`Long Cmp%`)==1,tour_pass.impute$`Long Cmp`/tour_pass.impute$`Long Att`,tour_pass.impute$`Long Cmp%`)
tour_pass.impute<-tour_pass.impute[,-c(5,8,13,16,19,23,29,30)]





#defense
#check the pos of corresponding player in tour_shoot
missing_player<-tour_defense %>% filter(is.na(tour_defense$Pos)==1)
pos<-tour_shoot1 %>% filter(Player==unlist(missing_player[1])) #GK
tour_defense$Pos<-ifelse(is.na(tour_defense$Pos)==1,unlist(pos[3]),tour_defense$Pos)

#remove useless data
tour_defense1<-tour_defense[,-c(5,7,16,22,30,31)]
colSums(is.na(tour_defense1))

#imputed dataset(optional)
#impute the missing values for Vs Dribble Tackles and Pressures % by definitions
tour_defense.impute<-tour_defense
tour_defense.impute$`Vs Dribbles Tkl%`<-ifelse(is.na(tour_defense.impute$`Vs Dribbles Tkl%`)==1,tour_defense.impute$`Vs Dribbles Tkl`/tour_defense.impute$`Vs Dribbles Att`,tour_defense.impute$`Vs Dribbles Tkl%`)

tour_defense.impute$`Pressures %`<-ifelse(is.na(tour_defense.impute$`Pressures %`)==1,tour_defense.impute$`Pressures Succ`/tour_defense.impute$`Pressures Press`,tour_defense.impute$`Pressures %`)

tour_defense.impute<-tour_defense.impute[,-c(5,7,16,22,30,31)]
colSums(is.na(tour_defense.impute))




#goalkeep

#remove useless data

tour_goalkeep1<-tour_goalkeep21[,-c(5,6,7,8,10,16,19,21,24,25,26)]
colSums(is.na(tour_goalkeep1))

#imputed dataset(optional)
#impute useful variable: Performance Save%
tour_goalkeep.impute<-tour_goalkeep21
tour_goalkeep.impute$`Performance Save%`<-ifelse(is.na(tour_goalkeep.impute$`Performance Save%`)==1,tour_goalkeep.impute$`Performance Saves`/tour_goalkeep.impute$`Performance SoTA`,tour_goalkeep.impute$`Performance Save%`)
tour_goalkeep.impute<-tour_goalkeep.impute[,-c(5,6,7,8,10,19,21,24,25,26)]
colSums(is.na(tour_goalkeep.impute))
```


## datasets:
tour_shoot1
tour_pass1
tour_defense1
tour_goalkeep1

```{r entropy weighted + regression, message=FALSE, warning=FALSE,tidy=TRUE,results='hide',eval=FALSE}

tour_defense1[,13] <- -tour_defense1[,13]
tour_goalkeep1[,c(11,13,15)] <- -tour_goalkeep1[,c(11,13,15)]

tour_shoot.FW1 <- tour_shoot1 %>% filter(grepl("FW", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Expected np:G-xG`, ~mean(.x, na.rm = TRUE)))

tour_pass.MF1 <- tour_pass1 %>% filter(grepl("MF", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE)))

tour_pass.FW1 <- tour_pass1 %>% filter(grepl("FW", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE)))

tour_pass.DF1 <- tour_pass1 %>% filter(grepl("DF", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE)))

tour_defense.DF1 <- tour_defense1 %>% filter(grepl("DF", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Err`, ~mean(.x, na.rm = TRUE)))

tour_defense.MF1 <- tour_defense1 %>% filter(grepl("MF", Pos)) %>% group_by(Nation) %>%
  summarise(across(`90s`:`Err`, ~mean(.x, na.rm = TRUE)))

tour_goalkeep.GK1 <- tour_goalkeep1 %>% group_by(Nation) %>% filter(grepl("GK", Pos)) %>%
  summarise(across(`Playing Time 90s`:`Penalty Kicks PKm`, ~mean(.x, na.rm = TRUE)))


## standardise

tour_shoot.FW.sd <- tour_shoot.FW1 %>%
  summarise(Nation, across(`90s`:`Expected np:G-xG`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_pass.MF.sd <- tour_pass.MF1 %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_pass.FW.sd <- tour_pass.FW1 %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_pass.DF.sd <- tour_pass.DF1 %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_defense.DF.sd <- tour_defense.DF1 %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_defense.MF.sd <- tour_defense.MF1 %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x-min(.x))/(max(.x)-min(.x))))

tour_goalkeep.GK.sd <- tour_goalkeep.GK1 %>%
  summarise(Nation, across(`Playing Time 90s`:`Penalty Kicks PKm`, ~(.x-min(.x))/(max(.x)-min(.x))))


## weights

tour_shoot.FW.w <- tour_shoot.FW.sd %>%
  summarise(Nation, across(`90s`:`Expected np:G-xG`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Expected np:G-xG`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Expected np:G-xG`, ~-sum(.x, na.rm = T)*log(nrow(tour_shoot.FW1))^(-1))) %>%
  summarise(across(`90s`:`Expected np:G-xG`, ~(1-.x)/(ncol(tour_shoot.FW1[,-1])-sum(.x))))

tour_pass.MF.w <- tour_pass.MF.sd %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Prog`, ~-sum(.x, na.rm = T)*log(nrow(tour_pass.MF1))^(-1))) %>%
  summarise(across(`90s`:`Prog`, ~(1-.x)/(ncol(tour_pass.MF1[,-1])-sum(.x))))

tour_pass.FW.w <- tour_pass.FW.sd %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Prog`, ~-sum(.x, na.rm = T)*log(nrow(tour_pass.FW1))^(-1))) %>%
  summarise(across(`90s`:`Prog`, ~(1-.x)/(ncol(tour_pass.FW1[,-1])-sum(.x))))

tour_pass.DF.w <- tour_pass.DF.sd %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Prog`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Prog`, ~-sum(.x, na.rm = T)*log(nrow(tour_pass.DF1))^(-1))) %>%
  summarise(across(`90s`:`Prog`, ~(1-.x)/(ncol(tour_pass.DF1[,-1])-sum(.x))))

tour_defense.DF.w <- tour_defense.DF.sd %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Err`, ~-sum(.x, na.rm = T)*log(nrow(tour_defense.DF1))^(-1))) %>%
  summarise(across(`90s`:`Err`, ~(1-.x)/(ncol(tour_defense.DF1[,-1])-sum(.x))))

tour_defense.MF.w <- tour_defense.MF.sd %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`90s`:`Err`, ~(.x*log(.x)))) %>%
  summarise(across(`90s`:`Err`, ~-sum(.x, na.rm = T)*log(nrow(tour_defense.MF1))^(-1))) %>%
  summarise(across(`90s`:`Err`, ~(1-.x)/(ncol(tour_defense.MF1[,-1])-sum(.x))))

tour_goalkeep.GK.w <- tour_goalkeep.GK.sd %>%
  summarise(Nation, across(`Playing Time 90s`:`Penalty Kicks PKm`, ~(.x/sum(.x)))) %>%
  summarise(Nation, across(`Playing Time 90s`:`Penalty Kicks PKm`, ~(.x*log(.x)))) %>%
  summarise(across(`Playing Time 90s`:`Penalty Kicks PKm`, ~-sum(.x, na.rm = T)*log(nrow(tour_goalkeep.GK1))^(-1))) %>%
  summarise(across(`Playing Time 90s`:`Penalty Kicks PKm`, ~(1-.x)/(ncol(tour_goalkeep.GK1[,-1])-sum(.x))))


## combine 6 dimensions

tour_shoot.FW2 <- as.matrix(tour_shoot.FW.sd[,-1]) %*% t(tour_shoot.FW.w)
tour_shoot.FW <- as.data.frame(cbind(tour_shoot.FW1$Nation, tour_shoot.FW2))
colnames(tour_shoot.FW) <- c("Nation", "ShootingFW")

tour_pass.MF2 <- as.matrix(tour_pass.MF.sd[,-1]) %*% t(tour_pass.MF.w)
tour_pass.MF <- as.data.frame(cbind(tour_pass.MF1$Nation, tour_pass.MF2))
colnames(tour_pass.MF) <- c("Nation", "PassingMF")

tour_pass.FW2 <- as.matrix(tour_pass.FW.sd[,-1]) %*% t(tour_pass.FW.w)
tour_pass.FW <- as.data.frame(cbind(tour_pass.FW1$Nation, tour_pass.FW2))
colnames(tour_pass.FW) <- c("Nation", "PassingFW")

tour_pass.DF2 <- as.matrix(tour_pass.DF.sd[,-1]) %*% t(tour_pass.DF.w)
tour_pass.DF <- as.data.frame(cbind(tour_pass.DF1$Nation, tour_pass.DF2))
colnames(tour_pass.DF) <- c("Nation", "PassingDF")

tour_defense.DF2 <- as.matrix(tour_defense.DF.sd[,-1]) %*% t(tour_defense.DF.w)
tour_defense.DF <- as.data.frame(cbind(tour_defense.DF1$Nation, tour_defense.DF2))
colnames(tour_defense.DF) <- c("Nation", "DefenseDF")

tour_defense.MF2 <- as.matrix(tour_defense.MF.sd[,-1]) %*% t(tour_defense.MF.w)
tour_defense.MF <- as.data.frame(cbind(tour_defense.MF1$Nation, tour_defense.MF2))
colnames(tour_defense.MF) <- c("Nation", "DefenseMF")

tour_goalkeep.GK2 <- as.matrix(tour_goalkeep.GK.sd[,-1]) %*% t(tour_goalkeep.GK.w)
tour_goalkeep.GK <- as.data.frame(cbind(tour_goalkeep.GK1$Nation, tour_goalkeep.GK2))
colnames(tour_goalkeep.GK) <- c("Nation", "GoalkeepingGK")

tour2021.all <- merge(tour_shoot.FW, tour_pass.MF, by = "Nation") %>%
  merge(tour_pass.FW, by = "Nation") %>% merge(tour_pass.DF, by = "Nation") %>%
  merge(tour_defense.DF, by = "Nation") %>% merge(tour_defense.MF, by = "Nation") %>%
  merge(tour_goalkeep.GK, by = "Nation")

tour_rank21 <- merge(tour2021.all, rank21, by.x = "Nation", by.y = "country")

## regression analysis

tour_rank21[,9] <- if_else(tour_rank21$rank21 > 10, 0, 1)
tour_rank21$`ShootingFW` <- as.numeric(tour_rank21$`ShootingFW`)
tour_rank21$`PassingMF` <- as.numeric(tour_rank21$`PassingMF`)
tour_rank21$`PassingFW` <- as.numeric(tour_rank21$`PassingFW`)
tour_rank21$`PassingDF` <- as.numeric(tour_rank21$`PassingDF`)
tour_rank21$`DefenseDF` <- as.numeric(tour_rank21$`DefenseDF`)
tour_rank21$`DefenseMF` <- as.numeric(tour_rank21$`DefenseMF`)
tour_rank21$`GoalkeepingGK` <- as.numeric(tour_rank21$`GoalkeepingGK`)

log1_rank21 <- glm(rank21 ~ ., family = "binomial", data = tour_rank21[,-1])
summary(log1_rank21)
stepAIC(log1_rank21)

rf1_rank21 <- randomForest(rank21 ~. , tour_rank21[,-1], method="rf", mtry=3, ntree=50)
varImpPlot(rf1_rank21, main = "Feature Importance")

N <- nrow(tour_rank21)
Acc_log <- Acc_log.shrink <- Acc_rf <- vector(length=N)

for(i in 1:N){
  train_set <- tour_rank21[-i,-1]
  vali_set <- tour_rank21[i,-1]
  
  # logistic regression
  log_rank21 <- glm(rank21 ~ .-`PassingMF`-`DefenseDF`, family = "binomial",
                    data = train_set)
  pred_log <- if_else(predict(log_rank21, vali_set, type = "response")>0.5,1,0)
  
  # logistic regression + shrinkage
  log.shrink_rank21 <- cv.glmnet(as.matrix(train_set[,-8]), train_set$rank21,
                                 family="binomial", alpha=0.5, nfolds = N)
  pred_log.shrink <- if_else(predict(log.shrink_rank21, s=log.shrink_rank21$lambda.min,
                                     newx=as.matrix(vali_set[,-8]), type="response")>0.5,1,0)
  
  # random forest
  # rf_rank21 <- randomForest(rank21 ~. , train_set, method="rf", mtry=3, ntree=50)
  # pred_rf <- if_else(predict(rf_rank21, vali_set)>0.5,1,0)
  
  Acc_log[i] <- if_else(vali_set[,8] == pred_log, 1, 0)
  Acc_log.shrink[i] <- if_else(vali_set[,8] == pred_log.shrink, 1, 0)
  #Acc_rf[i] <- if_else(vali_set[,8] == pred_rf, 1, 0)
  
}

sum(Acc_log)/N
sum(Acc_log.shrink)/N
# sum(Acc_rf)/N


```

```{r team selection, message=FALSE, warning=FALSE,tidy=TRUE,results='hide',eval=FALSE}

lea_shoot1 <- lea_shoot[,-c(6,9,10,15,21,22)]
lea_pass1 <- lea_pass[,-c(6,9,14,17,20,24)]
lea_defense1 <- lea_defense[,-c(6,8,17,23)]
lea_goalkeep1 <- lea_goalkeep[,-c(6,7,8,9,11,17,20,22,25)]

lea_defense1[,14] <- -lea_defense1[,14]
lea_goalkeep1[,c(12,14,16)] <- -lea_goalkeep1[,c(12,14,16)]

lea_shoot.FW1 <- lea_shoot1 %>% filter(grepl("FW", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Expected np:G-xG`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_pass.MF1 <- lea_pass1 %>% filter(grepl("MF", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_pass.FW1 <- lea_pass1 %>% filter(grepl("FW", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_pass.DF1 <- lea_pass1 %>% filter(grepl("DF", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Prog`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_defense.DF1 <- lea_defense1 %>% filter(grepl("DF", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Err`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_defense.MF1 <- lea_defense1 %>% filter(grepl("MF", Pos)) %>% group_by(Player) %>%
  summarise(across(`90s`:`Err`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

lea_goalkeep.GK1 <- lea_goalkeep1 %>% filter(grepl("GK", Pos)) %>% group_by(Player) %>%
  summarise(across(`Playing Time 90s`:`Penalty Kicks PKm`, ~mean(.x, na.rm = TRUE))) %>%
  na.omit()

## standardise

lea_shoot.FW.sd <- lea_shoot.FW1 %>%
  summarise(Player, across(`90s`:`Expected np:G-xG`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_pass.MF.sd <- lea_pass.MF1 %>%
  summarise(Player, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_pass.FW.sd <- lea_pass.FW1 %>%
  summarise(Player, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_pass.DF.sd <- lea_pass.DF1 %>%
  summarise(Player, across(`90s`:`Prog`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_defense.DF.sd <- lea_defense.DF1 %>%
  summarise(Player, across(`90s`:`Err`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_defense.MF.sd <- lea_defense.MF1 %>%
  summarise(Player, across(`90s`:`Err`, ~(.x-min(.x))/(max(.x)-min(.x))))

lea_goalkeep.GK.sd <- lea_goalkeep.GK1 %>%
  summarise(Player, across(`Playing Time 90s`:`Penalty Kicks PKm`, ~(.x-min(.x))/(max(.x)-min(.x))))

## score for each player

lea_shoot.FW2 <- as.matrix(lea_shoot.FW.sd[,-1]) %*% t(tour_shoot.FW.w)
lea_shoot.FW3 <- as.data.frame(cbind(lea_shoot.FW1$Player, lea_shoot.FW2))
colnames(lea_shoot.FW3) <- c("Player", "ShootingFW")
lea_shoot.FW <- cbind(filter(lea_shoot1, grepl("FW", Pos))[match(lea_shoot.FW3$Player, filter(lea_shoot1, grepl("FW", Pos))$Player), c(2,3)], lea_shoot.FW3)

lea_pass.MF2 <- as.matrix(lea_pass.MF.sd[,-1]) %*% t(tour_pass.MF.w)
lea_pass.MF3 <- as.data.frame(cbind(lea_pass.MF1$Player, lea_pass.MF2))
colnames(lea_pass.MF3) <- c("Player", "PassingMF")
lea_pass.MF <- cbind(filter(lea_pass1, grepl("MF", Pos))[match(lea_pass.MF3$Player, filter(lea_pass1, grepl("MF", Pos))$Player), c(2,3)], lea_pass.MF3)

lea_pass.FW2 <- as.matrix(lea_pass.FW.sd[,-1]) %*% t(tour_pass.FW.w)
lea_pass.FW3 <- as.data.frame(cbind(lea_pass.FW1$Player, lea_pass.FW2))
colnames(lea_pass.FW3) <- c("Player", "PassingFW")
lea_pass.FW <- cbind(filter(lea_pass1, grepl("FW", Pos))[match(lea_pass.FW3$Player, filter(lea_pass1, grepl("FW", Pos))$Player), c(2,3)], lea_pass.FW3)

lea_pass.DF2 <- as.matrix(lea_pass.DF.sd[,-1]) %*% t(tour_pass.DF.w)
lea_pass.DF3 <- as.data.frame(cbind(lea_pass.DF1$Player, lea_pass.DF2))
colnames(lea_pass.DF3) <- c("Player", "PassingDF")
lea_pass.DF <- cbind(filter(lea_pass1, grepl("DF", Pos))[match(lea_pass.DF3$Player, filter(lea_pass1, grepl("DF", Pos))$Player), c(2,3)], lea_pass.DF3)

lea_defense.DF2 <- as.matrix(lea_defense.DF.sd[,-1]) %*% t(tour_defense.DF.w)
lea_defense.DF3 <- as.data.frame(cbind(lea_defense.DF1$Player, lea_defense.DF2))
colnames(lea_defense.DF3) <- c("Player", "DefenseDF")
lea_defense.DF <- cbind(filter(lea_defense1, grepl("DF", Pos))[match(lea_defense.DF3$Player, filter(lea_defense1, grepl("DF", Pos))$Player), c(2,3)], lea_defense.DF3)

lea_defense.MF2 <- as.matrix(lea_defense.MF.sd[,-1]) %*% t(tour_defense.MF.w)
lea_defense.MF3 <- as.data.frame(cbind(lea_defense.MF1$Player, lea_defense.MF2))
colnames(lea_defense.MF3) <- c("Player", "DefenseMF")
lea_defense.MF <- cbind(filter(lea_defense1, grepl("MF", Pos))[match(lea_defense.MF3$Player, filter(lea_defense1, grepl("MF", Pos))$Player), c(2,3)], lea_defense.MF3)

lea_goalkeep.GK2 <- as.matrix(lea_goalkeep.GK.sd[,-1]) %*% t(tour_goalkeep.GK.w)
lea_goalkeep.GK3 <- as.data.frame(cbind(lea_goalkeep.GK1$Player, lea_goalkeep.GK2))
colnames(lea_goalkeep.GK3) <- c("Player", "GoalkeepingGK")
lea_goalkeep.GK <- cbind(filter(lea_goalkeep1, grepl("GK", Pos))[match(lea_goalkeep.GK3$Player, filter(lea_goalkeep1, grepl("GK", Pos))$Player), c(2,3)], lea_goalkeep.GK3)

# choosing players

lea_shoot.FW$`ShootingFW` <- as.numeric(lea_shoot.FW$`ShootingFW`)
lea_pass.MF$`PassingMF` <- as.numeric(lea_pass.MF$`PassingMF`)
lea_pass.FW$`PassingFW` <- as.numeric(lea_pass.FW$`PassingFW`)
lea_pass.DF$`PassingDF` <- as.numeric(lea_pass.DF$`PassingDF`)
lea_defense.DF$`DefenseDF` <- as.numeric(lea_defense.DF$`DefenseDF`)
lea_defense.MF$`DefenseMF` <- as.numeric(lea_defense.MF$`DefenseMF`)
lea_goalkeep.GK$`GoalkeepingGK` <- as.numeric(lea_goalkeep.GK$`GoalkeepingGK`)

tour_rarita.FW1 <- lea_shoot.FW %>% filter(ShootingFW > quantile(ShootingFW, 0.95)) %>% filter(Nation == "Rarita")
tour_rarita.DF1 <- lea_pass.DF %>% filter(PassingDF > quantile(PassingDF, 0.95)) %>% filter(Nation == "Rarita")
tour_rarita.MF1 <- lea_defense.MF %>% filter(DefenseMF > quantile(DefenseMF, 0.95)) %>% filter(Nation == "Rarita")
tour_rarita.GK1 <- lea_goalkeep.GK %>% filter(GoalkeepingGK > quantile(GoalkeepingGK, 0.95)) %>% filter(Nation == "Rarita")

tour_rarita.FW2 <- rbind(tour_rarita.FW1, lea_shoot.FW %>% arrange(desc(ShootingFW)) %>% slice(1:6))
tour_rarita.FW <- merge(tour_rarita.FW2, lea_pass.FW)
tour_rarita.DF <- merge(tour_rarita.DF1, lea_defense.DF)
tour_rarita.MF2 <- rbind(tour_rarita.MF1, lea_defense.MF %>% arrange(desc(DefenseMF)) %>% slice(1:3))
tour_rarita.MF <- merge(tour_rarita.MF2, lea_pass.MF)
tour_rarita.GK <- rbind(tour_rarita.GK1, lea_goalkeep.GK %>% arrange(desc(GoalkeepingGK)) %>% slice(1))

# team
team_rarita <- rbind(tour_rarita.FW[,c(1:3)], tour_rarita.DF[,c(1:3)], tour_rarita.MF[,c(1:3)],
                     tour_rarita.GK[,c(1:3)])

team_rarita.score <- data.frame(Nation = "Rarita", ShootingFW = mean(tour_rarita.FW$ShootingFW),
                   PassingMF = mean(tour_rarita.MF$PassingMF),
                   PassingDF = mean(tour_rarita.DF$PassingDF),
                   PassingFW = mean(tour_rarita.FW$PassingFW),
                   DefenseMF = mean(tour_rarita.MF$DefenseMF),
                   DefenseDF = mean(tour_rarita.DF$DefenseDF),
                   GoalkeepingGK = mean(tour_rarita.GK$GoalkeepingGK))

# prob of top 10
log_fit <- glm(rank21 ~ `ShootingFW`+`PassingFW`+`PassingDF`+`DefenseMF`+`GoalkeepingGK`,
               family = "binomial", data = tour_rank21[,-1]) 
summary(log_fit)
pred_rarita <- predict(log_fit, team_rarita.score, type = "response")
pred_rarita


```
```{r salaries, message=FALSE, warning=FALSE,tidy=TRUE,results='hide',eval=FALSE}
salary<-left_join(team_rarita,salary21,by=c("Player"="Player Name"))

add<-salary %>% filter(is.na(`Annualized Salary`)==1) %>% dplyr::select(Player,Nation,Pos) %>% left_join(salary20,by=c("Player"="Player Name"))

add$`Annualized Salary`<-add$`Annualized Salary`*1.02

salary1<-salary[-which(is.na(salary$`Annualized Salary`)),]
salary1<-rbind(add,salary1) %>% arrange(by="Pos")
salary1<-salary1[,-c(6,7)]

playercost<-salary1 %>% mutate(cost=ifelse(Nation=="Rarita",`Annualized Salary`,`Annualized Salary`*1.1))
playercost

#totol player expense
totalcost_player<-sum(playercost$cost)

#foreign player expense
totalcost_foreign_player<-playercost %>% filter(Nation!="Rarita") %>% summarise(total=sum(cost))

rent<-playercost %>% filter(Nation!="Rarita") %>% summarise(rent=sum(cost)-sum(`Annualized Salary`))
```



